Component response rate variation drives stability in large complex systems

### 2018-06-01 notebook/SI.Rmd
Fix spelling

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Different connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Different distributions of $\gamma$](#gam_dist)
- [Genetic algorithm](#ga) 
- [Feasilbility of complex systems](#Feasibility)

>>>>

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Different connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Different distributions of $\gamma$](#gam_dist)
- [Genetic algorithm](#ga) 
- [Feasibility of complex systems](#Feasibility)
